
---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tidyverse.quiet = TRUE)
```

# siconvr

<!-- badges: start -->
  [![CRAN status](https://www.r-pkg.org/badges/version/siconvr)](https://CRAN.R-project.org/package=tTIER)
  [![R-CMD-check](https://github.com/marcustorresz/TIER/workflows/R-CMD-check/badge.svg)](https://github.com/marcustorresz/TIER/actions)
[![Codecov test coverage](https://codecov.io/gh/marcustorresz/TIER/branch/main/graph/badge.svg)](https://codecov.io/gh/marcustorrez/TIER?branch=main)
[![Travis build status](https://travis-ci.com/marcustorresz/TIER.svg?branch=main)](https://travis-ci.com/marcustorresz/TIER)
<!-- badges: end -->


`TIER` is an R package to Provides documentation for your R project,
through version 4.0 of the TIER protocol, developed by project TIER.


## Installing

Install the package from CRAN using:

```{r, eval=FALSE}
install.packages("TIER")
```


To install the package's development version, use:

```{r, eval=FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("marcustorresz/TIER")
```





## How to use

Using `TIER` to help to organize you project is easy. Just use `tier_protocol` function and you are ready to go. 


## Contributing

We welcome any help to improve `TIER`. In case you wish to contribute with code, use [GitHub Pull Requests](https://docs.github.com/pt/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request) -- we will be more than happy to acknowledge any assistance by updating our authors' list. Bug reports and suggestions can be done via [GitHub issues](https://github.com/marcustorreszs/TIER/issues).



## Authors

[ Marcus Torres](https://marcustorresz.github.io/) and [Amanda Domingos]()

